{$\ch_2(\tf)$ Optimality Conditions for a Finite-time Horizon\thanksref{mytitlenote}}

### 2019-05-01 response.tex

\title{Authors' Response to the Referee Comments}
\author{}
\date{}
\begin{document}
\maketitle

We thank the referees {for their detailed reading of the manuscript and their valuable comments}.
 We have incorporated the changes that the referees have suggested into the revised
manuscript.   We list below the referees' comments, followed by our responses, denoted by \serkan{\textsf{AR}}.

\section*{Referee \#1}%change this about referee #1

\begin{itemize}
\item My only concern is the fact that the term H2 is used on time-domain
function, which might be inappropriate from a mathematical point of
view?\\
\serkan{\textsf{AR}: We thank the reviewer for this comment. Since the time domain and frequency domain functions are equivalent, we believe this notation is appropriate. Furthermore, since the infinite horizon, and finite horizon case appear to be connected, the notation $\mathcal{H}_2(t_f)$ illustrates this connection. We have explained further in the paper our choice of notation.
} 
\end{itemize}

@@

\end{itemize}

\section*{Referee \#3}

\begin{itemize}
\item As stated in Remark 3.2, the optimality condition is not directly
expressed by H(s) and Hr(s), but by G(s) and Gr(s), defined by (3.5)
and (3.7).  The reviewer cannot find a physical interpretation of G(s)
and Gr(s).  The authors can comment on the interpretation.\\
\serkan{\textsf{AR}:  We thank the referee for the insightful comment. We have addressed this issue on the revised version.}

\item In Numerical Simulation, the authors can add some time responses of
the original and reduced-order models.	For example, showing impulse
responses of the models enables readers to understand "practical"
importance of the proposed method.\\
\serkan{\textsf{AR}:  We thank the referee for the comment. We have added a graph showing the time responses for the error for different methods. Here are two additional graphs for two other models}
 \begin{figure}[H]
 \centering
   \includegraphics [scale=0.5]{absHeatErrorYlim}
      \caption{POD vs \FH for a heat model\label{fig:impulseHeat}}
 \end{figure}
 \begin{figure}[H]
 \centering
   \includegraphics [scale=0.5]{absUNSError}
      \caption{POD vs \FH for an unstable model\ \label{fig:impulseUns}}
 \end{figure}

### 2019-05-01 FH Optimality Conditions Paper.tex
added impulse plots

For all three models, we choose $t_f = 1$, first reduce the original model using POD, \goyal \  or TLBT, and then use the resulting reduced model  to initialize \FH. Thus, we are trying to investigate how these different initializations affect the final reduced model via  \FH \ and how much improvement one might expect.
The results are shown in Figures \ref{fig:hm}--\ref{fig:uns},  where we show the $\ch_2(\tf)$ approximation error for different values of $r$, the order of the reduced model.
  All three initializations are used for the heat model (Figure \ref{fig:hm}) where the order is reduced from $r=2$ to $r=10$ with increments of one. For some $r$ values, certain initializations are excluded (e.g., the \goyal \ initialization for $r=6$) since the algorithm either did not converge or produced  poor approximations. However, this happened rarely. For the ISS model (Figure \ref{fig:iss}), we use  TLBT and \goyal \ initializations since  POD produced very poor approximations and thus is excluded. In this case, we reduce the order from $r=2$ to $r=14$ with increments of $2$. For the unstable model (Figure \ref{fig:uns}), we use POD and \goyal \ initializations; for this model our implementation of TLBT produced  poor results and is avoided. In this case,  we reduce the order from $r=2$ to $r=12$ with increments of $2$.  
 The first observation is that,  since  \FH \ is a descent-method and drives the initialization to a local minimizer,  it improves the accuracy of  the reduced model for all three initializations as expected. The improvements could be dramatic. For example, 
 \FH \ is able to outperform POD as much as by an order of magnitude, see, for example,
 Figure \ref{fig:hm}, the  $r=4$ and $r=5$ cases. 
 While \FH \ improves TLBT and \goyal\ initialization as well, the improvements for the heat model are not as significant. However, for the ISS model,
\FH \ is able to improve the TLBT performance as much as $50\%$; see, e.g., Figure \ref{fig:iss}, the $r=8$ case. 
The best improvement of the \goyal \ initialization has occurred for the unstable model. For example, for $r=8$, for the unstable model, \FH\ improved the reduced model by more than $40 \%$. Gains were significantly better for POD, especially for larger $r$ values. 
% \begin{figure}[H] 
% \centering
% \begin{subfigure}{.5\textwidth}
% \centering
% \includegraphics [scale=0.4]{allDataHeatF} 
% \caption{\FH \ and other algorithms for a heat model\label{fig:hm}}
% \end{subfigure}
% \begin{subfigure}{.5\textwidth}
% \centering
% \includegraphics [scale=0.4]{ErrorVSrISSF}
% \caption{\FH \ and other algorithms for the ISS model \label{fig:iss}}
% \end{subfigure}
%  \begin{subfigure}{.5\textwidth}
% \centering
%   \includegraphics [scale=0.4]{ErrorVSrUNSF}
%      \caption{\FH \ and other algorithms for the unstable model \label{fig:uns}}
% \end{subfigure}
% \caption{Numerical results for three  models \label{mainfig}}
% \end{figure}

@@

 \begin{figure}%[H] 
 \centering
 \includegraphics [scale=0.5]{fig1h} 
 \caption{\FH \ and other algorithms for a heat model\label{fig:hm}}
 \end{figure}
 \begin{figure}%[H]
 \centering
  \includegraphics [scale=0.5]{fig2i}
 \caption{\FH \ and other algorithms for the heat model \label{fig:iss}}
 \end{figure}
  \begin{figure}%[H]
 \centering
   \includegraphics [scale=0.5]{fig3u}
      \caption{\FH \ and other algorithms for the ISS model \label{fig:uns}}
 \end{figure}

% \begin{figure}[H]
% \centering
%   \includegraphics [scale=0.4]{fig4}
%      \caption{\FH \ and other algorithms for the unstable model \label{fig:uns}}
% \end{figure}
%

@@

%\section*{References}
%\bibliographystyle{elsarticle-num}
\bibliographystyle{plain}

>>>>

For all three models, we choose $t_f = 1$, first reduce the original model using POD, \goyal \  or TLBT, and then use the resulting reduced model  to initialize \FH. Thus, we are trying to investigate how these different initializations affect the final reduced model via  \FH \ and how much improvement one might expect.
The results are shown in Figures \ref{fig:hm}--\ref{fig:uns},  where we show the $\ch_2(\tf)$ approximation error for different values of $r$, the order of the reduced model.
  All three initializations are used for the heat model (Figure \ref{fig:hm}) where the order is reduced from $r=2$ to $r=10$ with increments of one. For some $r$ values, certain initializations are excluded (e.g., the \goyal \ initialization for $r=6$) since the algorithm either did not converge or produced  poor approximations. However, this happened rarely. For the ISS model (Figure \ref{fig:iss}), we use  TLBT and \goyal \ initializations since  POD produced very poor approximations and thus is excluded. In this case, we reduce the order from $r=2$ to $r=14$ with increments of $2$. For the unstable model (Figure \ref{fig:uns}), we use POD and \goyal \ initializations; for this model our implementation of TLBT produced  poor results and is avoided. In this case,  we reduce the order from $r=2$ to $r=12$ with increments of $2$.  
 The first observation is that,  since  \FH \ is a descent-method and drives the initialization to a local minimizer,  it improves the accuracy of  the reduced model for all three initializations as expected. The improvements could be dramatic. For example, 
 \FH \ is able to outperform POD as much as by an order of magnitude, see, for example,
 Figure \ref{fig:hm}, the  $r=4$ and $r=5$ cases. 
 While \FH \ improves TLBT and \goyal\ initialization as well, the improvements for the heat model are not as significant. However, for the ISS model,
\FH \ is able to improve the TLBT performance as much as $50\%$; see, e.g., Figure \ref{fig:iss}, the $r=8$ case. 
The best improvement of the \goyal \ initialization has occurred for the unstable model. For example, for $r=8$, for the unstable model, \FH\ improved the reduced model by more than $40 \%$. Gains were significantly better for POD, especially for larger $r$ values. 
{\color{red} Also, in Figure \ref{impulse}, we compare the impulse responses of the error systems of POD and \FH \ for the ISS model. For both methods, POD and \FH\  the reduced model was of order $r=14$. As we can see from the graph, \FH \ clearly outperforms POD on the time interval $[0, 1]$.

}

% \begin{figure}[H] 
% \centering
% \begin{subfigure}{.5\textwidth}
% \centering
% \includegraphics [scale=0.4]{allDataHeatF} 
% \caption{\FH \ and other algorithms for a heat model\label{fig:hm}}
% \end{subfigure}
% \begin{subfigure}{.5\textwidth}
% \centering
% \includegraphics [scale=0.4]{ErrorVSrISSF}
% \caption{\FH \ and other algorithms for the ISS model \label{fig:iss}}
% \end{subfigure}
%  \begin{subfigure}{.5\textwidth}
% \centering
%   \includegraphics [scale=0.4]{ErrorVSrUNSF}
%      \caption{\FH \ and other algorithms for the unstable model \label{fig:uns}}
% \end{subfigure}
% \caption{Numerical results for three  models \label{mainfig}}
% \end{figure}

@@

 \begin{figure}[H] 
 \centering
 \includegraphics [scale=0.35]{fig1h} 
 \caption{\FH \ and other algorithms for a heat model\label{fig:hm}}
 \end{figure}
 \begin{figure}[H]
 \centering
  \includegraphics [scale=0.35]{fig2i}
 \caption{\FH \ and other algorithms for the heat model \label{fig:iss}}
 \end{figure}
  \begin{figure}[H]
 \centering
   \includegraphics [scale=0.35]{fig3u}
      \caption{\FH \ and other algorithms for the ISS model \label{fig:uns}}
 \end{figure}

 \begin{figure}[H]
 \centering
   \includegraphics [scale=0.35]{ISS1RErrorSmooth}
      \caption{\FH \ and other algorithms for the unstable model \label{fig:impulse}}
 \end{figure}

@@

%\section*{References}
%\bibliographystyle{elsarticle-num}

\bibliographystyle{plain}
